---
title: "Bioinformatics Rmd report"
author: "Elisha Bhattarai"
output: html_document
theme: cosmo
---

##Heading number 1 - download file and read into R
Here we're using the download.file()`command to obtain the dataset
then we're reading it in to R. It is important to set 'header=TRUE'
and 'row.names=1' so that the data is formatted properly

```{r,chunk1,echo=TRUE}
#Download the data
download.file("https://raw.githubusercontent.com/markziemann/SLE712_files/master/bioinfo_asst3_part1_files/mydata.tsv",
              destfile = "mydata.tsv")
              
#Read into R making sure the 1st column is set as the row names and headers are recognised
x <- read.table("mydata.tsv", header = TRUE , stringsAsFactors = FALSE, row.names =1) 
```

## Heading 2 - checking data iontegrity
Here we use the 'head()' command to look at the first 6 lines of the dataframe,then'str()' to make sure the contents are recognized as numeric.

```{r,chunk2,echo=TRUE}




## Heading 2
## Heading2 - checking data iontegrity



#Lets check if the data has been imported properly
head(x)



str(x)
